\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Arumalla Mohit Krishna}} \\
  New York, USA \\
  +1-631-352-8643 \enspace | \enspace marumalla@cs.stonybrook.edu \enspace | \enspace \href{https://linkedin.com/in/mohit-krishna-arumalla}{linkedin.com/in/mohit-krishna-arumalla}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Software Engineer} with 2+ years of experience specializing in building \textbf{high-performance distributed systems}, backend microservices, and \textbf{performance optimization}. Proficient in \textbf{Golang}, \textbf{C++}, and rapidly learning \textbf{Rust} to develop scalable, production-grade software. Experienced in distributed system design, real-time data pipelines, and resource optimization. Adept at delivering tested, robust solutions leveraging strong systems fundamentals including concurrency and memory management. Passionate about building interactive, efficient tools and collaborating with cross-functional teams using Agile methodologies.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Golang, C++, Rust (learning), Java, Python, JavaScript, SQL (PostgreSQL) \\
     \textbf{Backend and Cloud}: RESTful APIs, gRPC, Microservices, AWS (EC2, S3, Lambda), Docker, Kubernetes, Linux \\
     \textbf{Distributed Systems}: Apache Flink, Kafka, CDC, Raft Consensus, RDMA, Paxos, RPC, Concurrency, Synchronization \\
     \textbf{Performance Engineering}: CPU/GPU optimization, Memory Profiling, Low-latency Systems, Real-time Data Pipelines \\
     \textbf{Data and Visualization}: PostgreSQL, Elasticsearch, Redis, RocksDB, High-throughput Querying, Data Streaming \\
     \textbf{Development Practices}: Agile/Scrum, Automated Testing, Code Reviews, Performance Optimization, Clean Code \\
     \textbf{Collaborative Systems}: Real-time Data Sync, State Synchronization, Conflict Resolution Concepts
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Infra.Market}}{\textbf{Apr 2024 -- Aug 2025}}
      {Software Engineer II}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Developed scalable microservices with custom hierarchical location structure, full CRUD operations, Looker integration, and RESTful APIs for distributed location-based queries; implemented gRPC for efficient inter-service communication.}
        \resumeItem{Optimized backend service handling 50K+ daily queries, reducing memory by 70\% through Elasticsearch client optimization and Golang heap profiling; eliminated GC pauses and OOM errors in production.}
        \resumeItem{Designed real-time distributed data pipeline using Apache Flink, Kafka, and CDC, syncing 5M+ records with low latency via RocksDB state management and FlinkSQL, enabling near real-time querying and data processing.}
        \resumeItem{Built backend for dynamic indexing and faceted search; enabling 35\% faster product discovery for 200+ users, improving conversion rates.}
        \resumeItem{Architected AI-driven retrieval augmented generation system serving 100K+ monthly queries with Elasticsearch vector DB and AWS Titan Embeddings; improved result relevance and user satisfaction.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Infra.Market}}{\textbf{Jul 2023 -- Mar 2024}}
      {Software Engineer I}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Owned Search and Location microservices design and maintenance, delivering backend APIs with gRPC and REST endpoints for product discovery and geolocation across distributed cloud infrastructure.}
        \resumeItem{Resolved critical PostgreSQL connection leaks and validated fixes via concurrent load testing, ensuring system stability under high traffic and preventing deadlocks.}
        \resumeItem{Standardized API documentation via Swagger/OpenAPI across Golang microservices and deployed distributed tracing with New Relic for end-to-end monitoring and performance profiling.}
        \resumeItem{Developed data pipelines migrating denormalized datasets from BigQuery to Elasticsearch with query optimization and dynamic filtering, enhancing search efficiency.}
        \resumeItem{Implemented proactive automated monitoring and alerting systems for stale index detection across Elasticsearch and Airflow, supporting infrastructure reliability.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Science in Computer Science}{\textbf{Aug 2025 -- May 2027}}
      {Stony Brook University, New York, USA}{GPA: 4.0/4.0}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework}: Database Systems, Analysis of Algorithms, Transformer Architectures \& LLMs}
      \resumeItemListEnd
    \resumeSubheading
      {Bachelor of Engineering in Electronics \& Communication}{\textbf{Aug 2019 -- July 2023}}
      {Birla Institute of Technology and Science, Pilani, India}{GPA: 8.02/10}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework}: Object Oriented Programming, Operating Systems, Data Structures \& Algorithms, Computer Networks}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{RDMA-Accelerated Distributed Transactions} -- \emph{C++, RDMA, Distributed Systems}}{\textbf{Nov 2025 -- Ongoing}}
          \resumeItemListStart
            \resumeItem{Architecting RDMA integration for distributed transaction replication targeting 30-50\% latency reduction and 40-60\% CPU improvement over TCP/IP by implementing one-sided RDMA operations for Paxos-based log shipping.}
            \resumeItem{Designing remote memory layout and RDMA connection management with both two-sided verbs and one-sided operations for commit notifications, researching Motor (OSDI '24), FaRM, and DrTM for low-latency protocols.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Raft Consensus Protocol} -- \emph{C++, RPC, Distributed Systems}}{\textbf{Sept 2025 -- Nov 2025}}
          \resumeItemListStart
            \resumeItem{Implemented Raft consensus algorithm in C++ achieving distributed consensus across 5-node clusters with leader election, log replication, and fault tolerance maintaining 99.9\% availability under network partitions and split-brain scenarios.}
            \resumeItem{Built custom RPC protocol with RequestVote and AppendEntries handlers, managing timeouts and ensuring sub-5-second leader election with consistent state replication.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Elasticsearch Configuration Service} -- \emph{Golang, Elasticsearch}}{\textbf{Apr 2025 -- Jul 2025}}
          \resumeItemListStart
            \resumeItem{Engineered platform abstraction layer with self-serve RESTful APIs for Elasticsearch operations, enabling teams to provision search infrastructure efficiently without specialized expertise.}
            \resumeItem{Designed Golang backend services for automated index lifecycle management, schema versioning, and query optimization, reducing setup time by 70\% with infrastructure-as-code and rollback capabilities.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}