\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Arumalla Mohit Krishna}} \\
  New York, USA \\
  +1-631-352-8643 \enspace | \enspace marumalla@cs.stonybrook.edu \enspace | \enspace \href{https://linkedin.com/in/mohit-krishna-arumalla}{linkedin.com/in/mohit-krishna-arumalla}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Software Engineer} with 2+ years of experience building \textbf{scalable distributed systems} and backend microservices, specializing in designing and developing robust full-stack solutions. Proficient in \textbf{Golang}, \textbf{C++}, and \textbf{Apache Flink} with strong skills in API design, cloud infrastructure, and real-time data pipelines. Experienced in collaborating with cross-functional teams using Agile methodologies to deliver high-impact, production-grade software. Passionate about quick learning, navigating ambiguity, and contributing to AI-driven workflows and code generation systems.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Golang (Production), C++ (Distributed Systems), Python, JavaScript, SQL (PostgreSQL) \\
     \textbf{Backend and Cloud}: RESTful APIs, gRPC, Microservices, AWS (EC2, S3, Lambda, Titan), Docker, Kubernetes, Linux \\
     \textbf{Distributed Systems}: Apache Flink, Kafka, CDC, Raft Consensus, RDMA, Paxos, RPC \\
     \textbf{Data and AI}: Elasticsearch, Vector DBs, RAG, ML Pipelines, Real-time Aggregation, AI-driven Code Generation \\
     \textbf{DevOps}: CI/CD, NGINX, New Relic, Airflow, Performance Profiling, Swagger/OpenAPI, Automated Testing \\
     \textbf{Networking}: TCP/IP, DNS, DHCP, RDMA, Network Performance Optimization \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Performance Optimization, Product Ownership 
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Infra.Market}}{\textbf{Apr 2024 -- Aug 2025}}
      {Software Engineer II}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Developed scalable microservices with hierarchical location structures, full CRUD APIs, Looker integration, and gRPC communication enhancing distributed service interaction.}
        \resumeItem{Optimized high-traffic backend service reducing memory usage by 70\%, eliminating GC pauses and out of memory errors, ensuring robust production stability.}
        \resumeItem{Designed real-time distributed data pipeline using Apache Flink, Kafka, and CDC to sync millions of records with sub-second latency leveraging RocksDB state management.}
        \resumeItem{Built backend for Deal Mining Workbench with dynamic indexing and faceted search, improving data discovery efficiency and user engagement.}
        \resumeItem{\textbf{Architected production AI-driven RAG system leveraging Elasticsearch vector DB and AWS Titan embeddings, boosting query relevance and customer satisfaction significantly.}}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Infra.Market}}{\textbf{Jul 2023 -- Mar 2024}}
      {Software Engineer I}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Owned design and maintenance of Search and Location microservices delivering APIs via gRPC and REST, supporting product discovery and geolocation in distributed cloud environments.}
        \resumeItem{Resolved critical PostgreSQL connection leaks and validated concurrency fixes through load testing to ensure system reliability under heavy load.}
        \resumeItem{Standardized API documentation with Swagger/OpenAPI and deployed distributed tracing via New Relic for end-to-end observability.}
        \resumeItem{Built efficient Airflow data pipelines migrating denormalized datasets from BigQuery to Elasticsearch enhancing query performance and dynamic filtering.}
        \resumeItem{\textbf{Implemented automated monitoring solutions with Slack alerts for stale index detection enabling proactive infrastructure and data pipeline management.}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Science in Computer Science}{\textbf{Aug 2025 -- May 2027}}
      {Stony Brook University, New York, USA}{GPA: 4.0/4.0}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework}: Database Systems, Analysis of Algorithms, Transformer Architectures \& LLMs}
      \resumeItemListEnd
    \resumeSubheading
      {Bachelor of Engineering in Electronics \& Communication}{\textbf{Aug 2019 -- July 2023}}
      {Birla Institute of Technology and Science, Pilani, India}{GPA: 8.02/10}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework}: Object Oriented Programming, Operating Systems, Data Structures \& Algorithms, Computer Networks}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{RDMA-Accelerated Distributed Transactions} -- \emph{C++, RDMA, Distributed Systems}}{\textbf{Nov 2025 -- Ongoing}}
          \resumeItemListStart
            \resumeItem{Architecting RDMA integration for distributed transaction replication targeting 30-50\% latency reduction and 40-60\% CPU improvement over TCP/IP by implementing one-sided RDMA operations for Paxos-based log shipping.}
            \resumeItem{Designing remote memory layout and RDMA connection management with both two-sided verbs and one-sided operations for commit notifications, researching Motor (OSDI '24), FaRM, and DrTM for low-latency protocols.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Raft Consensus Protocol} -- \emph{C++, RPC, Distributed Systems}}{\textbf{Sept 2025 -- Nov 2025}}
          \resumeItemListStart
            \resumeItem{Implemented Raft consensus algorithm in C++ achieving distributed consensus across 5-node clusters with leader election, log replication, and fault tolerance maintaining 99.9\% availability under network partitions and split-brain scenarios.}
            \resumeItem{Built custom RPC protocol with RequestVote and AppendEntries handlers, managing timeouts and ensuring sub-5-second leader election with consistent state replication.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Elasticsearch Configuration Service} -- \emph{Golang, Elasticsearch}}{\textbf{Apr 2025 -- Jul 2025}}
          \resumeItemListStart
            \resumeItem{Engineered platform abstraction layer with self-serve RESTful APIs for Elasticsearch operations, enabling teams to provision search infrastructure without specialized expertise.}
            \resumeItem{Designed Golang backend services for automated index lifecycle management, schema versioning, and query optimization, reducing setup time by 70\% with infrastructure-as-code and rollback capabilities.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}