\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Arumalla Mohit Krishna}} \\
  New York, USA \\
  +1-631-352-8643 \enspace | \enspace marumalla@cs.stonybrook.edu \enspace | \enspace \href{https://linkedin.com/in/mohit-krishna-arumalla}{linkedin.com/in/mohit-krishna-arumalla}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Detail-oriented \textbf{Software Engineer} with 2+ years of experience in building and maintaining \textbf{scalable backend systems}, microservices, and real-time data pipelines. Skilled in programming languages including \textbf{C++}, \textbf{Python}, and \textbf{Golang}, with strong foundation in \textbf{data structures, algorithms}, and \textbf{software design principles}. Experienced in collaborating within Agile teams, contributing to code reviews, and writing automated tests. Passionate about applying software engineering skills in dynamic, hands-on environments and eager to contribute to innovative, impactful projects.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: C++, Python, Golang, Java, JavaScript, SQL (PostgreSQL) \\
     \textbf{Tools \& IDEs}: Visual Studio, Git, Eclipse, Docker, Kubernetes, Linux, AWS \\
     \textbf{Software Development}: Agile/Scrum, RESTful APIs, gRPC, Microservices, CI/CD, Code Reviews, Automated Testing \\
     \textbf{Distributed Systems}: Apache Flink, Kafka, CDC, Raft Consensus, RPC, RDMA Optimization \\
     \textbf{Data Management}: PostgreSQL, Elasticsearch, Redis, RocksDB, Vector DBs \\
     \textbf{Scripting \& Automation}: Bash, Python scripting for task automation \\
     \textbf{Networking \& System Design}: TCP/IP, DNS, DHCP, Performance Profiling, System Design Principles
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Infra.Market}}{\textbf{Apr 2024 -- Aug 2025}}
      {Software Engineer II}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Developed scalable microservices with hierarchical location structure, full CRUD, Looker integration, and RESTful APIs supporting distributed location-based queries; implemented \textbf{gRPC} for service communication.}
        \resumeItem{Optimized backend service handling 50K+ daily queries, reducing memory by 70\% through Elasticsearch client optimization and Golang heap profiling; eliminated GC pauses and OOM errors in production environment.}
        \resumeItem{Designed and maintained real-time distributed data pipelines using Apache Flink, Kafka, and CDC to sync 5M+ records from PostgreSQL to Elasticsearch; improved latency from 10-15 min to sub-second using RocksDB as state backend and FlinkSQL.}
        \resumeItem{Built backend for Deal Mining Workbench with dynamic indexing and faceted search, increasing search speed 35\% for 200+ users and improving user experience.}
        \resumeItem{\textbf{Collaborated cross-functionally} across teams to integrate new services and improve automation, enhancing system reliability and development workflow efficiency.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Infra.Market}}{\textbf{Jul 2023 -- Mar 2024}}
      {Software Engineer I}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Owned design and maintenance of Search and Location microservices, developing backend APIs with \textbf{gRPC} and REST endpoints to support product discovery and geolocation features across cloud infrastructure.}
        \resumeItem{Resolved PostgreSQL connection leaks by analyzing Gorm ORM behavior; conducted concurrency stress tests to ensure stability and prevent deadlocks under high traffic conditions.}
        \resumeItem{Standardized API documentation using Swagger/OpenAPI for Golang microservices and deployed New Relic distributed tracing, facilitating performance monitoring and debugging.}
        \resumeItem{Developed \textbf{Airflow} pipelines to migrate denormalized datasets from BigQuery to Elasticsearch, optimizing queries and enabling dynamic filtering for improved search performance.}
        \resumeItem{Implemented automated monitoring with Slack alerts for detecting stale indexes across Elasticsearch, BigQuery, and Airflow workflows, enabling proactive maintenance and reducing downtime.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Science in Computer Science}{\textbf{Aug 2025 -- May 2027}}
      {Stony Brook University, New York, USA}{GPA: 4.0/4.0}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework}: Database Systems, Analysis of Algorithms, Transformer Architectures \& LLMs}
      \resumeItemListEnd
    \resumeSubheading
      {Bachelor of Engineering in Electronics \& Communication}{\textbf{Aug 2019 -- July 2023}}
      {Birla Institute of Technology and Science, Pilani, India}{GPA: 8.02/10}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework}: Object Oriented Programming, Operating Systems, Data Structures \& Algorithms, Computer Networks}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{RDMA-Accelerated Distributed Transactions} -- \emph{C++, RDMA, Distributed Systems}}{\textbf{Nov 2025 -- Ongoing}}
          \resumeItemListStart
            \resumeItem{Architecting RDMA integration for distributed transaction replication targeting 30-50\% latency reduction and 40-60\% CPU improvement over TCP/IP by implementing one-sided RDMA operations for Paxos-based log shipping.}
            \resumeItem{Designing remote memory layout and RDMA connection management with both two-sided verbs and one-sided operations for commit notifications, researching Motor (OSDI '24), FaRM, and DrTM for low-latency protocols.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Raft Consensus Protocol} -- \emph{C++, RPC, Distributed Systems}}{\textbf{Sept 2025 -- Nov 2025}}
          \resumeItemListStart
            \resumeItem{Implemented Raft consensus algorithm in C++ achieving distributed consensus across 5-node clusters with leader election, log replication, and fault tolerance maintaining 99.9\% availability under network partitions and split-brain scenarios.}
            \resumeItem{Built custom RPC protocol with RequestVote and AppendEntries handlers, managing timeouts and ensuring sub-5-second leader election with consistent state replication.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Elasticsearch Configuration Service} -- \emph{Golang, Elasticsearch}}{\textbf{Apr 2025 -- Jul 2025}}
          \resumeItemListStart
            \resumeItem{Engineered platform abstraction layer with self-serve RESTful APIs for Elasticsearch operations, enabling teams to provision search infrastructure without specialized expertise.}
            \resumeItem{Designed Golang backend services for automated index lifecycle management, schema versioning, and query optimization, reducing setup time by 70\% with infrastructure-as-code and rollback capabilities.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}